Output Summary

### 2022-01-26 03-post-process/output-plots.Rmd
Improve MCMC diagnostics

## Diagnostic Summaries

```{r make-diag-post}
# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
# there is no point in calculating diagnostic summaries for future years
if (length(simulated) > 0) {
  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
} else {
  diag_post = post
}
```

@@

diag_fn = function(params, L1 = NA, L2 = NA, L3 = NA) {

  # extract the posteriors of interest and format for 'posterior' package
  post_sub = as_draws_df(post_subset(diag_post, params))

@@

@@

  # summarize the summaries
  out = data.frame(
    L1 = L1,
    L2 = L2,
    L3 = L3,
    match = params,
    n_params = nrow(diags),
    Rhat_1.05 = sum(diags$rhat >= 1.05),
    Rhat_1.1 = sum(diags$rhat >= 1.1),
    Rhat_1.2 = sum(diags$rhat >= 1.2),
    ess_mean_400 = sum(diags$ess_mean < 400),
    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
  )

  # return the summarized summaries
  return(out)
}

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# LH apportionment
L1 = "Life History Apportionment"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
pi_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# parr survival from summer to winter tagging
L1 = "Survival From Summer to Winter"
match = c("phi_Pb_Pa[2,.]")
phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))

# Overwinter survival
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants")))
match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants")))
phi_Pa_Mb_diags = rbind(tmp1, tmp2)

# Migration survival: trib to LGR
L1 = "Migration Survival (Trib to LGR)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
phi_Mb_Ma_diags = rbind(tmp1, tmp2)

# Migration survival: LGR to BON
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor)
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
tmp3 = diag_fn("rho_Lphi_Ma_O0[2,1]", L1 = "Migration Survival (LGR to Ocean)", L2 = "Among-origin Correlation")
phi_Ma_O0_diags = rbind(tmp1, tmp2, tmp3)

# Probability of Maturing at Age-3
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O1_diags = rbind(tmp1, tmp2)

# Probability of Maturing at Age-4
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O2_diags = rbind(tmp1, tmp2)

# Year 1 ocean survival
L1 = "Year 1 Ocean Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Year 2 ocean survival
L1 = "Year 2&3 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O1_O2[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
base = c("delta[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Migration survival: BON to LGR
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor)
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
tmp3 = diag_fn("rho_Lphi_Rb_Ra[2,1]", L1 = "Migration Survival (BON to LGR)", L2 = "Among-origin Correlation")
phi_Rb_Ra_diags = rbind(tmp1, tmp2)

# Pre-spawn Survival
L1 = "Pre-spawn Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "phi_Sb_Sa[.+,.]")
phi_Sb_Sa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Carcass Correction
L1 = "Carcass Correction Factor"
L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
z_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Initial adult recruitment
L1 = "Initial Adult Returns"
L2 = c("Age-3", "Age-4", "Age-5")
match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[[i]], L1 = L1, L2 = L2[i])))

# Straying
L1 = "Strays"
L2 = c("Realized Total Number", "Age Comp")
match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
G_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_diags,
  psi_O2_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  G_diags
)

# remove any summaries for nodes that don't have diagnostics
# e.g., if that "parameter" takes on a fixed value in the model
diags_table = diags_table[diags_table$n_params > 0,]
```

This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model. Values in cells represent the percentage of parameters of a given type that fail a diagnostic check. E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had Rhat values greater than 1.05. Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.

* **Rhat** measures convergence of multiple chains to a common target distribution. Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should not be used for inference (general rules).
* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al. [2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.

@@

```{r mcmc-diag-table}
# duplicate the diagnostic output
kable_table = diags_table

>>>>

## Sampling Diagnostics {.tabset .tabset-pills}

```{r make-diag-post}
# make a reduced diagnostic posterior: drop out all quantities associated with simulated years
# there is no point in calculating diagnostic summaries for future years
if (length(simulated) > 0) {
  diag_post = suppressMessages(post_remove(post, paste0("[", simulated), ask = FALSE))
} else {
  diag_post = post
}

# discard duplicate correlation terms: all rho parameters for a given process are equal
all_rho = match_params(post, "^rho")
rho_keep = match_params(post, "^rho_.+[2,1")
rho_discard = all_rho[!(all_rho %in% rho_keep)]
diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
```

@@

summarize_posterior = function(params, L1 = NA, L2 = NA, L3 = NA) {
  # extract the posteriors of interest and format for 'posterior' package
  post_sub = as_draws_df(post_subset(diag_post, params))

@@

  # append the level names and return
  cbind(
    L1 = L1, L2 = L2, L3 = L3,
    diags
  )
}

summarize_diags = function(diags) {

@@

  # summarize the summaries
  data.frame(
    L1 = unique(diags$L1),
    L2 = unique(diags$L2),
    L3 = unique(diags$L3),
    match = unique(postpack:::drop_index(diags$variable)),
    n_params = nrow(diags),
    Rhat_1.01 = sum(diags$rhat >= 1.01),
    Rhat_1.05 = sum(diags$rhat >= 1.05),
    Rhat_1.1 = sum(diags$rhat >= 1.1),
    Rhat_1.2 = sum(diags$rhat >= 1.2),
    ess_mean_400 = sum(diags$ess_mean < 400),
    ess_q2.5_400 = sum(diags$ess_q2.5 < 400),
    ess_q97.5_400 = sum(diags$ess_q97.5 < 400),
    mccv_mean_0.05 = sum(diags$mccv_mean > 0.05),
    mccv_q2.5_0.05 = sum(diags$mccv_q2.5 > 0.05),
    mccv_q97.5_0.05 = sum(diags$mccv_q97.5 > 0.05)
  )
}
```

```{r calculate-mcmc-diagnostics}
# containers
diags_out = NULL
summs_out = NULL

# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized")
match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LH apportionment
L1 = "Life History Apportionment"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_pi[1,.]", "sig_Lpi", "rho_Lpi", "^pi[.+,1,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# parr survival from summer to winter tagging
L1 = "Survival From Summer to Winter"
match = c("phi_Pb_Pa[2,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Fall Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_fall, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Fall Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Overwinter survival: Spring Migrants
L1 = "Overwinter Survival"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
base = list("gamma0[LH_type,pop]", "gamma1[LH_type,pop]", "sig_Lphi_Pa_Mb[LH_type,pop]", "rho_Lphi_Pa_Mb[.,.,LH_type]", "^phi_Pa_Mb[year,LH_type,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "Spring Migrants"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# trib to LGR Migration survival: NOR 
L1 = "Migration Survival (Trib to LGR)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# trib to LGR Migration survival: HOR 
L1 = "Migration Survival (Trib to LGR)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = list("mu_phi_Mb_Ma[LH_type,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", "rho_Lphi_Mb_Ma[.,.,origin]", "phi_Mb_Ma[year,LH_type,origin,pop]")
match = sub_index(base, year = ".+", LH_type = i_spring, origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival: NOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival: HOR
L1 = "Migration Survival (LGR to Ocean)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Ma_O0[origin]", "sig_Lphi_Ma_O0[origin]", "phi_Ma_O0[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival correlation among origins
tmp_diags = summarize_posterior("rho_Lphi_Ma_O0[2,1]", L1 = L1, L2 ="Among-origin Correlation")
tmp_summ =  summarize_diags(tmp_diags)
diags_out = rbind(diags_out, tmp_diags)
summs_out = rbind(summs_out, tmp_summ)

# Probability of Maturing at Age-3: NOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-3: HOR
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: NOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Probability of Maturing at Age-4: HOR
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 1 ocean survival
L1 = "Year 1 Ocean Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 2 ocean survival
L1 = "Year 2&3 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O1_O2[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
base = c("delta[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# BON to LGR Migration survival: NOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "NOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# BON to LGR Migration survival: HOR 
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_hor)
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i], L3 = "HOR"))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# LGR to Ocean Migration survival correlation among origins
tmp_diags = summarize_posterior("rho_Lphi_Rb_Ra[2,1]", L1 = L1, L2 ="Among-origin Correlation")
tmp_summ =  summarize_diags(tmp_diags)
diags_out = rbind(diags_out, tmp_diags)
summs_out = rbind(summs_out, tmp_summ)

# Pre-spawn Survival
L1 = "Pre-spawn Survival"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
match = c("mu_phi_Sb_Sa[.]", "sig_Lphi_Sb_Sa[.]", "rho_Lphi_Sb_Sa", "phi_Sb_Sa[.+,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Carcass Correction
L1 = "Carcass Correction Factor"
L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Initial adult recruitment
L1 = "Initial Adult Returns"
L2 = c("Age-3", "Age-4", "Age-5")
match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Straying
L1 = "Strays"
L2 = c("Realized Total Number", "Age Comp")
match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# remove any summaries for nodes that don't have diagnostics
# e.g., if that "parameter" takes on a fixed value in the model
diags_table = summs_out
diags_table = diags_table[diags_table$n_params > 0,]
```

### Summary Table

This table displays summaries of MCMC diagnostics for all unobserved stochastic nodes in the model. Values in cells represent the percentage of parameters of a given type that fail a diagnostic check. E.g., 50% in the "Rhat > 1.05" column means that half of the parameters of that type had $\hat{R}$ values greater than 1.05. Cells with no color indicate no offense and darker reds indicate greater frequency of an offense.

* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution. Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al. [2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.

@@

```{r mcmc-diag-table, warning = FALSE}
# duplicate the diagnostic output
kable_table = diags_table
